Computational musicology, ????, Profit

### 2016-07-23 paper.tex
Clean up some algomusicology references and add more important references.

A common interpretation of the Gnomes' business is as a satire on Silicon Valley startups.
Algomusicologists and starter-uppers have a challenge in common with the Underpants Gnomes
- we may have collected and analysed a considerable quantity of underpants/music/users, but how are we to profit from that?

@@

This paper will argue that it can. It will do so by reviewing existing literary and musical works that are informed by algorithmic
thinking, and also by using algomusicological concepts to create a new work that challenges our present conception of musical
authorship and copyright. As befits its subject matter, this paper will incorporate conventions and style from literary essays
and musicology papers.

@@

The duo Autechre responded with the Anti EP\cite{Anti EP}, whose third track `Flutter', was designed to protest the legislation.
Band member
Sean Booth explained that they ``made as many different bars as we could on the drum machine, then strung them all together."
\cite{Joseph Gallivan on pop}
In other words, as every bar features a unique beat, `Flutter' does not match the government's algomusicological description
of ``repetitive beats".

@@

Both legislators and artists are clearly taking algomusicological positions. The government attempted to construct the set
of all rave musics using a complexity characterisation. Autechre responded with what amounts to a diagonal argument, demonstrating
the inadequacy of the original claim.

@@

Here we finally come to the profit generation strategy - copyright litigation. As the \verb|copyright-infringement-song| is
a universal piece of music, any work published subsequent to it infringes on its copyright.~\footnote{I am not a lawyer. Do not rely on my legal advice.} In order to convert our algomusicological understanding into profit, we simply have to sue the composers
of every marginally successful musical work from now until they fix the law.

@@

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone, \url{https://overtone.github.io}.
\bibitem{Anti EP} Autechre (Rob Brown and Sean Booth): Anti EP, \textit{Warp Records}, 1994.
\bibitem{The Library of Babel} Borges, Jorge Luis: `The Library of Babel' in The Garden of Forking Paths, \textit{Editorial Sur}, 1941.
\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt: Gnomes, Episode 17, Season 2 of \textit{South Park}, 1998.
\bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten, \textit{Journal of the London Mathematical Society}, volume 8, 1933.
\bibitem{Leipzig} Ford, Chris: Leipzig, \url{https://github.com/ctford/leipzig}.
\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop, \textit{The Independent}, July 18, 1994.
\bibitem{Got to Give It Up} Gaye, Marvin: Got to Give It Up, \textit{Tamla}, 1977.
\bibitem{Clojure} Hickey, Rich: Clojure, \url{http://clojure.org/}
\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers, \textit{Sankhyā Series A}, volume 25, 1963.
\bibitem{Midje} Marick, Brian: Midje, \url{https://github.com/marick/Midje}.
\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression, \textit{The Music Encoding Conference}, 2013.
\bibitem{USA Today} Oldenburg, Ann: `Blurred Lines' jury finds for Marvin Gaye, \textit{USA Today}, March 11, 2015.
\bibitem{Contact} Sagan, Carl: Contact, \textit{Simon and Schuster}, 1985.
\bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{Communications of the ACM}, volume 58, issue 12, 2015.
\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines, \textit{Star Trak Recordings}, 2013.

>>>>

A common interpretation of the Gnomes' business is as a satire on Silicon Valley startups.
Computational musicologists and starter-uppers have a challenge in common with the Underpants Gnomes
- we may have collected and analysed a considerable quantity of underpants/music/users, but how are we to profit from that?

@@

This paper will argue that it can. It will do so by reviewing existing literary and musical works that are informed by algorithmic
thinking, and also by using computational musicological concepts to create a new work that challenges our present conception of musical
authorship and copyright. As befits its subject matter, this paper will incorporate conventions and style from literary essays
and musicology papers.

@@

The duo Autechre responded with the Anti EP\cite{Anti EP}, whose third track `Flutter', was designed to protest the legislation.
Band member
Sean Booth explained that they ``made as many different bars as we could on the drum machine, then strung them all together."
\cite{Joseph Gallivan on pop}
In other words, as every bar features a unique beat, `Flutter' does not match the government's computational musicological description
of ``repetitive beats".

@@

Both legislators and artists are clearly taking computational musicological positions. The government attempted to construct the set
of all rave musics using a complexity characterisation. Autechre responded with what amounts to a diagonal argument, demonstrating
the inadequacy of the original claim.

@@

Here we finally come to the profit generation strategy - copyright litigation. As the \verb|copyright-infringement-song| is
a universal piece of music, any work published subsequent to it infringes on its copyright.~\footnote{I am not a lawyer. Do not rely on my legal advice.} In order to convert our computational musicology understanding into profit, we simply have to sue the composers
of every marginally successful musical work from now until they fix the law.

@@

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone, \url{https://overtone.github.io}.
\bibitem{Anti EP} Autechre (Rob Brown and Sean Booth): Anti EP, \textit{Warp Records}, 1994.
\bibitem{The Library of Babel} Borges, Jorge Luis: `The Library of Babel' in The Garden of Forking Paths, \textit{Editorial Sur}, 1941.
\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt: Gnomes, Episode 17, Season 2 of \textit{South Park}, 1998.
\bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten, \textit{Journal of the London Mathematical Society}, volume 8, 1933.
\bibitem{Computational Musicology} Eduardo Coutinho, Marcelo Gimenes, Joao M. Martins and Eduardo R. Miranda: TODO. 
\bibitem{Three Paradigms of Computer Science} Eden, Amnon. TODO.
\bibitem{Leipzig} Ford, Chris: Leipzig, \url{https://github.com/ctford/leipzig}.
\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop, \textit{The Independent}, July 18, 1994.
\bibitem{Got to Give It Up} Gaye, Marvin: Got to Give It Up, \textit{Tamla}, 1977.
\bibitem{Clojure} Hickey, Rich: Clojure, \url{http://clojure.org/}
\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers, \textit{Sankhyā Series A}, volume 25, 1963.
\bibitem{Midje} Marick, Brian: Midje, \url{https://github.com/marick/Midje}.
\bibitem{The Digital Computer as a Musical Instrument} Mathews, M. V., \textid{Science}, 1963. TODO.
\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression, \textit{The Music Encoding Conference}, 2013.
\bibitem{Music, Mind and Meaning} Minsky, Marvin. 1981.
\bibitem{USA Today} Oldenburg, Ann: `Blurred Lines' jury finds for Marvin Gaye, \textit{USA Today}, March 11, 2015.
\bibitem{Contact} Sagan, Carl: Contact, \textit{Simon and Schuster}, 1985.
\bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{Communications of the ACM}, volume 58, issue 12, 2015.
\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines, \textit{Star Trak Recordings}, 2013.
